---
title: "TMDB Box Office Prediction"
subtitle: Kaggle Competition
Author: Meenal Narsinghani(meenal19)
output:
  html_document:
    df_print: paged
    toc: true
    toc_depth: 6
    collapsed: false
---



### Initial setup


#### Loading the necessary packages
```{r, warning=FALSE, error=FALSE, message=FALSE}
library(tidyverse)
library(readr)
library(lubridate)
library(ggplot2)
library(plotly)
library(randomForest)
library(stringi)
library(gbm)
```

#### Loading the train and test datasets
```{r}
train.data <- read.csv("train.csv", na.strings = c("", 0, '[]', '#N/A'))

test.data <- read.csv('test.csv', na.strings = c("", 0, '[]', '#N/A'))

dim(train.data)
dim(test.data)
```

#### Combining the test and train datasets for analysis
```{r}
test.data$revenue <- NA
complete.data <- rbind(train.data, test.data)

glimpse(complete.data)

colnames(complete.data)[1] <- gsub('^...','',colnames(complete.data)[1])

```


Based on the initial glimpse of the dataset, we notice:

* Columns like `tmdb_id`, `poster_path` are not relevant for this analysis
* Columns like `genres`, `production_companies`, `Keywords`, `cast` need to be cleaned as they have multiple information stored in single cell
* Columns like `tagline`, `homepage` can have indicator flags associated


### Feature Engineering

#### Irrelevant Features

**Dropping columns imdb_id, poster_path from our analytical dataset**
```{r}
complete.data <- complete.data %>% 
                    select(-c("imdb_id",
                              "poster_path"))
```


#### Indicator Variables
Considering the nature of variables: `homepage`, `tagline`, `overview`, `belongs_to_collection`, we will be creating indicator variables for these 
```{r}
complete.data <- complete.data %>% 
                    mutate(has_homepage = ifelse(is.na(homepage),"no" , "yes"),
                           has_overview = ifelse(is.na(overview), "no" , "yes"),
                           has_tagline = ifelse(is.na(tagline), "no", "yes"),
                           part_of_collection = ifelse(is.na(belongs_to_collection), "no", "yes"))

#Dropping the original columns
complete.data <- complete.data %>% 
                    select(-c("homepage", "overview", "tagline", "belongs_to_collection"))
```

Cleaning up following columns by creating derived variables

* genres
* production_companies
* production_countries
* spoken_languages
* Keywords
* cast
* crew

#### Genres

* Creating a new variable `total_genres` to store the count of total number of genres for each movie
* Creating indicator variables corresponding to each genre

```{r}
#Counting the total number of genres for each movie
complete.data$total_genres <- str_count(complete.data$genres, pattern = 'name')

#Flagging indicators variables as 1 or 0 if the movie is of a particular genre or not
complete.data$genre_adv <-  ifelse(stri_detect_fixed(complete.data$genres, 'Adventure'),1, 0)
complete.data$genre_ani <-  ifelse(stri_detect_fixed(complete.data$genres, 'Animation'),1, 0)
complete.data$genre_fam <-  ifelse(stri_detect_fixed(complete.data$genres, 'Family'),1, 0)
complete.data$genre_fty <-  ifelse(stri_detect_fixed(complete.data$genres, 'Fantasy'),1, 0)
complete.data$genre_hor <-  ifelse(stri_detect_fixed(complete.data$genres, 'Horror'),1, 0)
complete.data$genre_sci <-  ifelse(stri_detect_fixed(complete.data$genres, 'Science Fiction'),1, 0)
complete.data$genre_com <-  ifelse(stri_detect_fixed(complete.data$genres, 'Comedy'),1, 0)
complete.data$genre_rom <-  ifelse(stri_detect_fixed(complete.data$genres, 'Romance'),1, 0)
complete.data$genre_dra <-  ifelse(stri_detect_fixed(complete.data$genres, 'Drama'),1, 0)
complete.data$genre_war <-  ifelse(stri_detect_fixed(complete.data$genres, 'War'),1, 0)
complete.data$genre_mys <-  ifelse(stri_detect_fixed(complete.data$genres, 'Mystery'),1, 0)
complete.data$genre_his <-  ifelse(stri_detect_fixed(complete.data$genres, 'History'),1, 0)
complete.data$genre_doc <-  ifelse(stri_detect_fixed(complete.data$genres, 'Documentary'),1, 0)
complete.data$genre_thl <-  ifelse(stri_detect_fixed(complete.data$genres, 'Thriller'),1, 0)
complete.data$genre_cri <-  ifelse(stri_detect_fixed(complete.data$genres, 'Crime'),1, 0)
complete.data$genre_act <-  ifelse(stri_detect_fixed(complete.data$genres, 'Action'),1, 0)
complete.data$genre_wes <-  ifelse(stri_detect_fixed(complete.data$genres, 'Western'),1, 0)
complete.data$genre_mus <-  ifelse(stri_detect_fixed(complete.data$genres, 'Music'),1, 0)
complete.data$genre_fgn <-  ifelse(stri_detect_fixed(complete.data$genres, 'Foreign'),1, 0)
complete.data$genre_tvm <-  ifelse(stri_detect_fixed(complete.data$genres, 'TV Movie'),1, 0)
```

#### Production Companies

* Creating a new variable `total_prod_comp` to store the count of total number of production companies associated with a movie
* Identifying the main production company of movies: `main_prod_comp`

```{r}
##Creating variable for number of production companies
complete.data$tot_prod_comp <- str_count(complete.data$production_companies, pattern = 'name') 

#Extracting the main prodcution company
for (i in 1:length(complete.data$production_companies))
{
  complete.data$main_prod_comp[i] <- substr(complete.data$production_companies[i],  str_locate(complete.data$production_companies[i],"name")[,1]+8, (str_locate_all(complete.data$production_companies[i],"'")[[1]][4])-1)
}

```


#### Production Countries

* Creating a new variable `total_prod_country` to store the count of total number of production countries associated with a movie
* Identifying the main production country of movies: `main_prod_country`

```{r}

##Creating variable for number of production countries
complete.data$tot_prod_country <- str_count(complete.data$production_countries, pattern = 'name') 

#Extracting the main prodcution country
for (i in 1:length(complete.data$production_countries))
{
  complete.data$main_prod_country[i] <- substr(complete.data$production_countries[i], str_locate(complete.data$production_countries[i],"name")[,1]+8, (str_locate_all(complete.data$production_countries[i],"'")[[1]][8])-1)
}

```

#### Spoken Languages

Creating variable `tot_language` to store the count of total spoken languages
```{r}
complete.data$tot_language <- str_count(complete.data$spoken_languages, pattern = 'name') 
```


#### Keywords
Creating variable `tot_keywords` to store the count of total spoken languages
```{r}
##Creating variable for number of keywords associated
complete.data$tot_keywords <- str_count(complete.data$Keywords, pattern = 'name') 
```


#### Cast

Creating variables `tot_cast`, `tot_female_cast` and `tot_male_cast` to store count of total cast, total female cast and total male cast respectively
```{r}
complete.data$tot_cast <- str_count(complete.data$cast, pattern = 'name') 
complete.data$tot_female_cast <- str_count(complete.data$cast, pattern = "'gender': 1") 
complete.data$tot_male_cast <- str_count(complete.data$cast, pattern = "'gender': 2") 
```

#### Crew

Creating variables `tot_crew`, `tot_female_crew` and `tot_male_crew` to store count of total crew, total female crew and total male crew respectively

```{r}
complete.data$tot_crew <- str_count(complete.data$crew, pattern = 'name') 
complete.data$tot_female_crew <- str_count(complete.data$crew, pattern = "'gender': 1") 
complete.data$tot_male_crew <- str_count(complete.data$crew, pattern = "'gender': 2") 
```


Dropping original variables:

* genres
* production_companies
* production_countries
* spoken_languages
* Keywords
* cast
* crew

```{r}
analysis_data <- complete.data %>%
                  select(-c("genres", 
                            "production_companies",
                            "spoken_languages",
                            "Keywords",
                            "cast",
                            "crew"))
```


#### Status
```{r}
table((analysis_data$status))
#Since majority of the movies have same status, removing the column from our analysis

analysis_data$status <- NULL
```


#### Original title and title 

Dropping these columns
```{r}
analysis_data$original_title <- NULL
analysis_data$title <- NULL
```


#### Release date

Determining the day, month, year and quarter when the movie was released. Also, flagging movie whether it was released on a weekend(Friday/Saturday/Sunday) or not
```{r}
analysis_data$weekday <- weekdays(as.Date(analysis_data$release_date,format="%m/%d/%y"))

analysis_data$is_weekend <- ifelse(analysis_data$weekday %in% c("Friday","Saturday","Sunday"), "yes","no")

analysis_data$release_month <- as.factor(month(as.Date(analysis_data$release_date, format = "%m/%d/%y")))

analysis_data$release_year <- year(as.Date(analysis_data$release_date, format = "%m/%d/%y"))

analysis_data$release_quarter <- as.factor(quarter(as.Date(analysis_data$release_date, format = "%m/%d/%y")))

##Dropping release_date
analysis_data$release_date <- NULL
```

#### Original Language

Creating a variable to categorize movie as English or non-English
```{r}
table(analysis_data$original_language)

analysis_data$language[analysis_data$original_language == 'en'] <- "English"
analysis_data$language[is.na(analysis_data$language == 'en')] <- "Non-English"

analysis_data$original_language <- NULL
```

***

### Exploratory Data Analysis & Missing Values treatment
**Univariate analysis and Feature Selection**

***

**Understanding the relationship between each predictor variable and the response variable `revenue`**

* **Revenue**

```{r}
summary(analysis_data$budget)

##Imputing the missing values of *budget* with the median budget value
analysis_data$budget[is.na(analysis_data$budget)] <- median(analysis_data$budget, na.rm = T)

```


```{r}
ggplot(data = analysis_data, aes(x = budget, fill = ..x..))+
  geom_histogram(bins = 20) +
    theme_classic() +
      scale_x_continuous(breaks = c(5000000,100000000,150000000, 200000000,250000000, 300000000,350000000,400000000),
                         labels = c('$5', '$10','$15' ,'$20', '$25','$30', '$35','$40')) +
        theme(legend.position = 'none') +
          ylab("Total number of movies") +
            xlab("Budget (in Millions)") 
#+
#              title("Frequency distribution of Budget")
```


Relationship between `revenue` and `budget`
```{r}
ggplot(data = analysis_data[1:3000,], aes(x= budget, y = revenue, color = budget))+
  geom_point() +
      geom_smooth(method = "lm", color = "darkred", fill = "red") +
        theme_light() +
          scale_x_continuous(breaks = c(5000000,100000000,150000000, 200000000,250000000, 300000000,350000000,400000000),
                              labels = c('$5', '$10','$15' ,'$20', '$25','$30', '$35','$40')) +
            scale_y_continuous(breaks = c(0, 500000000, 1000000000, 1500000000),
                               labels = c('$0', '$500', '$1000', '$1500')) +
              theme(legend.position = 'none') +
                  labs(title = "Relationship between Movie Budget and Revenue", 
                       x = "Budget($Millions",
                       y = "Revenue($Millions)")
```

```{r}
# ggplot(data = analysis_data, aes(x = revenue, fill = ..x..))+
#   geom_histogram() +
#     theme_classic()
```

* **Popularity**

```{r}
sum(is.na(analysis_data$popularity))
##No missing values
```

Relationship between `revenue` and `popularity`
```{r}
ggplot(data = analysis_data[1:3000,], aes(x= popularity, y = revenue, color = popularity))+
  geom_point(col = "#330066")+
      geom_smooth(method = "lm", color = "darkred", fill = "grey10") +
        theme_light() +
          scale_y_continuous(breaks = c(0, 500000000, 1000000000, 1500000000),
                             labels = c('$0', '$500', '$1000', '$1500')) +
              theme(legend.position = 'none') +
                labs(title = "Relationship between Movie Popularity and Revenue", 
                     x = "Popularity",
                     y = "Revenue($Millions)")
```


* **Runtime**

```{r}
#Checking for number of missing values
sum(is.na(analysis_data$runtime))
summary(analysis_data$runtime)

#Imputing the missing runtime values with median runtime value
analysis_data$runtime[is.na(analysis_data$runtime)] <- mean(analysis_data$popularity, na.rm = T)

ggplot(data = analysis_data, aes(x = runtime, fill = ..x..))+
  geom_histogram() +
    scale_x_continuous(limits = c(0,250)) +
    theme_classic()

```


Relation between *revenue* and *runtime*
```{r}
ggplot(data = analysis_data[1:3000,], aes(x= runtime, y = revenue, color = runtime))+
  geom_point() +
      geom_smooth(method = "lm", color = "darkred", fill = "red") +
        theme_light() +
            labs(title = "Relationship between Movie Length and Revenue", 
                 y = "Revenue($Millions)")
```

* **Total..**

*Spoken Languages*
```{r}
summary(analysis_data$tot_language)

table(analysis_data$tot_language)

#Imputing missing tot_language with the median
analysis_data$tot_language[is.na(analysis_data$tot_language)] <- 1

ggplot(data = analysis_data[1:3000,], aes(x = as.factor(tot_language), y = revenue)) +
  geom_boxplot()
```

*Keywords*
```{r}

sum(is.na(analysis_data$tot_keywords))
summary(analysis_data$tot_keywords)
table(analysis_data$tot_keywords)

analysis_data$tot_keywords[is.na(analysis_data$tot_keywords)] <- median(analysis_data$tot_keywords, na.rm = T)

ggplot(data = analysis_data, aes(x = tot_keywords, fill = ..x..))+
  geom_histogram() +
    theme_classic()


ggplot(data = analysis_data[1:3000,], aes(x= tot_keywords, y = revenue, color = tot_keywords))+
  geom_point() +
      geom_smooth(method = "lm", color = "darkred", fill = "red") +
        theme_light() +
            labs(title = "Relationship between Total Keywords and Revenue", 
                 y = "Revenue($Millions)")
```

*Cast, Female_Cast, Male_Cast*

```{r}
sum(is.na(analysis_data$tot_cast))
summary(analysis_data$tot_cast)
table(analysis_data$tot_cast)

ggplot(data = analysis_data, aes(x = tot_cast))+
  geom_histogram() + 
    geom_vline(data = analysis_data, aes(xintercept = mean(tot_cast, na.rm = T)), colour='black') + 
      geom_vline(data = analysis_data, aes(xintercept = median(tot_cast, na.rm = T)), colour='red') 

analysis_data$tot_cast[is.na(analysis_data$tot_cast)] <- median(analysis_data$tot_cast, na.rm = T)

ggplot(data = analysis_data[1:3000,], aes(x= tot_cast, y = revenue, color = tot_cast))+
  geom_point() +
      geom_smooth(method = "lm", color = "darkred", fill = "red") +
        theme_light() +
            labs(title = "Relationship between Total Cast and Revenue", 
                 y = "Revenue($Millions)")
```


```{r}
sum(is.na(analysis_data$tot_female_cast))
analysis_data$tot_female_cast[is.na(analysis_data$tot_female_cast)] <- median(analysis_data$tot_female_cast, na.rm = T)

ggplot(data = analysis_data[1:3000,], aes(x= tot_female_cast, y = revenue, color = tot_female_cast))+
  geom_point() +
      geom_smooth(method = "lm", color = "darkred", fill = "red") +
        theme_light() +
            labs(title = "Relationship between Total Female Cast and Revenue", 
                 y = "Revenue($Millions)")
```


```{r}
sum(is.na(analysis_data$tot_male_cast))
analysis_data$tot_male_cast[is.na(analysis_data$tot_male_cast)] <- median(analysis_data$tot_male_cast, na.rm = T)

ggplot(data = analysis_data[1:3000,], aes(x= tot_male_cast, y = revenue, color = tot_male_cast))+
  geom_point() +
      geom_smooth(method = "lm", color = "darkred", fill = "red") +
        theme_light() +
            labs(title = "Relationship between Total Male Cast and Revenue", 
                 y = "Revenue($Millions)")

```

*Crew, Female_Crew, Male_Crew*

```{r}
sum(is.na(analysis_data$tot_crew))
analysis_data$tot_crew[is.na(analysis_data$tot_crew)] <- median(analysis_data$tot_crew, na.rm = T)

ggplot(data = analysis_data[1:3000,], aes(x= tot_crew, y = revenue, color = tot_crew))+
  geom_point() +
      geom_smooth(method = "lm", color = "darkred", fill = "red") +
        theme_light() +
            labs(title = "Relationship between Total Crew and Revenue", 
                 y = "Revenue($Millions)")
```


```{r}
sum(is.na(analysis_data$tot_female_crew))

analysis_data$tot_female_crew[is.na(analysis_data$tot_female_crew)] <- median(analysis_data$tot_female_crew, na.rm = T)

ggplot(data = analysis_data[1:3000,], aes(x= tot_female_crew, y = revenue, color = tot_female_crew))+
  geom_point() +
      geom_smooth(method = "lm", color = "darkred", fill = "red") +
        theme_light() +
            labs(title = "Relationship between Total Female Crew and Revenue", 
                 y = "Revenue($Millions)")
```


```{r}
sum(is.na(analysis_data$tot_male_crew))
analysis_data$tot_male_crew[is.na(analysis_data$tot_male_crew)] <- median(analysis_data$tot_male_crew, na.rm = T)

ggplot(data = analysis_data[1:3000,], aes(x= tot_male_crew, y = revenue, color = tot_male_crew))+
  geom_point() +
      geom_smooth(method = "lm", color = "darkred", fill = "red") +
        theme_light() +
            labs(title = "Relationship between Total Male Crew and Revenue", 
                 y = "Revenue($Millions)")

```

*Genres*
```{r}
sum(is.na(analysis_data$total_genres))
table(analysis_data$total_genres)
summary(analysis_data$total_genres)

analysis_data$total_genres[is.na(analysis_data$total_genres)] <- median(analysis_data$total_genres, na.rm = T)


ggplot(data = analysis_data[1:3000,], aes(x = as.factor(total_genres), y = revenue)) +
  geom_boxplot()

```


***

**Categorical Variables**

*Language*
```{r}
ggplot(data = analysis_data, aes(x = language, fill = language))+
  geom_bar()
```

```{r,warning=FALSE, error=FALSE}
ggplot(data = analysis_data[1:3000,], aes(x = language, y = revenue)) +
  geom_boxplot()
```

**Homepage**
```{r}
ggplot(data = analysis_data[1:3000,], aes(x = as.factor(has_homepage), y = revenue)) +
  geom_boxplot()
```


**Overview**
```{r}
ggplot(data = analysis_data[1:3000,], aes(x = as.factor(has_overview), y = revenue)) +
  geom_boxplot()

```

**Tagline**
```{r}
ggplot(data = analysis_data[1:3000,], aes(x = as.factor(has_tagline), y = revenue)) +
  geom_boxplot() 

```

**Main Genre**
```{r}

# sum(is.na(analysis_data$main_genre))
# table(analysis_data$main_genre)
# 
# analysis_data$main_genre[is.na(analysis_data$main_genre)] <- 'Drama'

# ggplot(data = analysis_data[1:3000,], aes(x = main_genre, fill = main_genre))+
  # geom_bar()+
    #scale_fill_brewer(palette = 3) +
      # coord_flip() +
      #   theme_classic()
```


```{r}
# ggplot(analysis_data[1:3000,],  aes(x = main_genre,  y = revenue, fill = main_genre)) + 
   # stat_summary_bin(fun.y = median, geom = "bar") +
    # coord_flip()
```


**Time of release**
```{r}
ggplot(analysis_data[1:3000,],  aes(x = as.factor(weekday),  y = revenue, fill = weekday)) + 
   stat_summary_bin(fun.y = median, geom = "bar")

```

```{r}
ggplot(analysis_data[1:3000,],  aes(x = as.factor(is_weekend),  y = revenue, fill = as.factor(is_weekend))) + geom_boxplot()
```

```{r}

ggplot(analysis_data[1:3000,],  aes(x = as.factor(release_month),  y = revenue, fill = as.factor(release_month))) + 
   stat_summary_bin(fun.y = median, geom = "bar")

```

```{r}

ggplot(data = analysis_data[1:3000,], aes(x= release_year, y = revenue, color = release_year))+
  geom_point() +
      geom_smooth(method = "lm", color = "darkred", fill = "red") +
        theme_light() +
            labs(title = "Relationship between Release Year and Revenue", 
                 y = "Revenue($Millions)")

```

Production Companies

```{r}
analysis_data %>% group_by(main_prod_comp) %>% count() %>% arrange(desc(n))

big_producer <- c("Universal Pictures",
                  "Paramount Pictures",
                  "Twentieth Century Fox Film Corporation",
                  "Columbia Pictures",
                  "New Line Cinema",
                  "Warner Bros.",		
                  "Walt Disney Pictures",
                  "Metro-Goldwyn-Mayer (MGM)",		
                  "Columbia Pictures Corporation")

analysis_data$production_comp <- ifelse(analysis_data$main_prod_comp %in% big_producer, "Big", "Small")

sum(is.na(analysis_data$production_comp))
analysis_data$main_prod_comp <- NULL

ggplot(analysis_data[1:3000,],  aes(x = production_comp,  y = revenue, fill = production_comp)) + geom_boxplot()


summary(analysis_data$tot_prod_comp)
table(analysis_data$tot_prod_comp)

analysis_data$tot_prod_comp[is.na(analysis_data$tot_prod_comp)] <- median(analysis_data$tot_prod_comp, na.rm = T)

```


Production Countries

```{r}
analysis_data %>% group_by(main_prod_country) %>% count() %>% arrange(desc(n))

big_country <- c("United States of America",
                  "United Kingdom",
                  "France",
                  "Canada",
                  "Germany",
                  "India")

analysis_data$US <- ifelse(analysis_data$main_prod_country == "United States of America", 1,0)
analysis_data$UK <- ifelse(analysis_data$main_prod_country == "United Kingdom", 1,0)
analysis_data$FR <- ifelse(analysis_data$main_prod_country == "France", 1,0)
analysis_data$CA <- ifelse(analysis_data$main_prod_country == "Canada", 1,0)
analysis_data$GR <- ifelse(analysis_data$main_prod_country == "Germany", 1,0)
analysis_data$IN <- ifelse(analysis_data$main_prod_country == "India", 1,0)
analysis_data$OT <- ifelse(!analysis_data$main_prod_country %in% big_country , 1,0)


#analysis_data$big_country <- ifelse(analysis_data$main_prod_country %in% big_country, "Big", "Small")

#sum(is.na(analysis_data$big_country))
analysis_data$main_prod_country <- NULL
analysis_data$production_countries <- NULL

#ggplot(analysis_data[1:3000,],  aes(x = big_country,  y = revenue, fill = big_country)) + geom_boxplot()


summary(analysis_data$tot_prod_country) 
analysis_data$tot_prod_country[is.na(analysis_data$tot_prod_country)] <- median(analysis_data$tot_prod_country, na.rm = T)


```

```{r}
apply(is.na(analysis_data),2,sum)
```

```{r}
analysis_data$US[is.na(analysis_data$US)] <- 0
analysis_data$UK[is.na(analysis_data$UK)] <- 0
analysis_data$FR[is.na(analysis_data$FR)] <- 0
analysis_data$CA[is.na(analysis_data$CA)] <- 0
analysis_data$GR[is.na(analysis_data$GR)] <- 0
analysis_data$IN[is.na(analysis_data$IN)] <- 0
```

```{r}
analysis_data$genre_act[is.na(analysis_data$genre_act)] <- 0
analysis_data$genre_adv[is.na(analysis_data$genre_adv)] <- 0
analysis_data$genre_ani[is.na(analysis_data$genre_ani)] <- 0
analysis_data$genre_fam[is.na(analysis_data$genre_fam)] <- 0
analysis_data$genre_fty[is.na(analysis_data$genre_fty)] <- 0
analysis_data$genre_hor[is.na(analysis_data$genre_hor)] <- 0
analysis_data$genre_sci[is.na(analysis_data$genre_sci)] <- 0
analysis_data$genre_com[is.na(analysis_data$genre_com)] <- 0
analysis_data$genre_rom[is.na(analysis_data$genre_rom)] <- 0

analysis_data$genre_dra[is.na(analysis_data$genre_dra)] <- 1

analysis_data$genre_war[is.na(analysis_data$genre_war)] <- 0
analysis_data$genre_mys[is.na(analysis_data$genre_mys)] <- 0
analysis_data$genre_his[is.na(analysis_data$genre_his)] <- 0
analysis_data$genre_doc[is.na(analysis_data$genre_doc)] <- 0
analysis_data$genre_thl[is.na(analysis_data$genre_thl)] <- 0
analysis_data$genre_cri[is.na(analysis_data$genre_cri)] <- 0
analysis_data$genre_wes[is.na(analysis_data$genre_wes)] <- 0
analysis_data$genre_mus[is.na(analysis_data$genre_mus)] <- 0
analysis_data$genre_fgn[is.na(analysis_data$genre_fgn)] <- 0
analysis_data$genre_tvm[is.na(analysis_data$genre_tvm)] <- 0

```

```{r}
summary(analysis_data$release_month)
analysis_data$release_month[is.na(analysis_data$release_month)] <- median(as.numeric(analysis_data$release_month), na.rm = T)

analysis_data$release_quarter[is.na(analysis_data$release_quarter)] <- median(as.numeric(analysis_data$release_quarter), na.rm = T)

analysis_data$release_year[is.na(analysis_data$release_year)] <- median(analysis_data$release_year, na.rm = T)

table(analysis_data$weekday)
analysis_data$weekday[is.na(analysis_data$weekday)] <- "Wednesday"
```


Estimating the missing budget values
```{r}

```




Subsetting the data for model fitting
```{r}
analysis_data$has_homepage <- as.factor(analysis_data$has_homepage)
analysis_data$has_overview <- as.factor(analysis_data$has_overview)
analysis_data$has_tagline <- as.factor(analysis_data$has_tagline)
analysis_data$part_of_collection <- as.factor(analysis_data$part_of_collection)
analysis_data$weekday <- as.factor(analysis_data$weekday)
analysis_data$is_weekend <- as.factor(analysis_data$is_weekend)
analysis_data$release_month <- as.factor(analysis_data$release_month)
analysis_data$release_quarter <- as.factor(analysis_data$release_quarter)
#analysis_data$main_genre <- as.factor(analysis_data$main_genre)
analysis_data$production_comp <- as.factor(analysis_data$production_comp)
analysis_data$language <- as.factor(analysis_data$language)
#analysis_data$big_country <- as.factor(analysis_data$big_country)
analysis_data$US <- as.factor(analysis_data$US)
analysis_data$UK <- as.factor(analysis_data$UK)
analysis_data$FR <- as.factor(analysis_data$FR)
analysis_data$CA <- as.factor(analysis_data$CA)
analysis_data$GR <- as.factor(analysis_data$GR)
analysis_data$IN <- as.factor(analysis_data$IN)
analysis_data$OT <- as.factor(analysis_data$OT)

# analysis_data[, grep("genre_", colnames(analysis_data))] <- as.factor(analysis_data[, grep("genre_", colnames(analysis_data))])

analysis_data$genre_act <- as.factor(analysis_data$genre_act)
analysis_data$genre_adv <- as.factor(analysis_data$genre_adv)
analysis_data$genre_ani <- as.factor(analysis_data$genre_ani)
analysis_data$genre_fam <- as.factor(analysis_data$genre_fam)
analysis_data$genre_fty <- as.factor(analysis_data$genre_fty)
analysis_data$genre_hor <- as.factor(analysis_data$genre_hor)
analysis_data$genre_sci <- as.factor(analysis_data$genre_sci)
analysis_data$genre_com <- as.factor(analysis_data$genre_com)
analysis_data$genre_rom <- as.factor(analysis_data$genre_rom)
analysis_data$genre_dra <- as.factor(analysis_data$genre_dra)
analysis_data$genre_war <- as.factor(analysis_data$genre_war)
analysis_data$genre_mys <- as.factor(analysis_data$genre_mys)
analysis_data$genre_his <- as.factor(analysis_data$genre_his)
analysis_data$genre_doc <- as.factor(analysis_data$genre_doc)
analysis_data$genre_thl <- as.factor(analysis_data$genre_thl)
analysis_data$genre_cri <- as.factor(analysis_data$genre_cri)
analysis_data$genre_wes <- as.factor(analysis_data$genre_wes)
analysis_data$genre_mus <- as.factor(analysis_data$genre_mus)
analysis_data$genre_fgn <- as.factor(analysis_data$genre_fgn)
analysis_data$genre_tvm <- as.factor(analysis_data$genre_tvm)

glimpse(analysis_data)
train.data <- analysis_data[1:3000,]

```


Model
```{r}

apply(is.na(train.data),2,sum)
glimpse(train.data)

model.rf <- randomForest( log10(revenue) ~ . , data = train.data,
                          ntree = 500,
                          importance = T)
model.rf

summary(model.rf)

importance <- importance(model.rf)
varImpPlot(model.rf)

model.rf$importance


plot(model.rf$mse, type='l', col=2, lwd=2, xlab = "ntree", ylab = "OOB Error")



# oob.err<- rep(0, 13)
# test.err<- rep(0, 13)
# for(i in 1:13){
  # fit<- randomForest(medv~., data = boston.train, mtry=i)
#   oob.err[i]<- fit$mse[500]
#   test.err[i]<- mean((boston.test$medv-predict(fit, boston.test))^2)
#   cat(i, " ")
# }
```




```{r}
test.data <- analysis_data[3001:7398,]
prediction <- predict(model.rf, test.data)
write.csv(10^prediction, "predicted_revenue.csv")
```

